An indexed construction of semi-simplicial and semi-cubical types

### 2022-05-18 paper/paper.tex
paper: finish off the easy part of the xkeyval conversion

% Truncated sets, otherwise referred to as X: the general macro
\newcommandx{\X}[2][1=,2=]{\ensuremath{\mathsf{\color{carolina}{X}}_{#1}^{#2}}}

% Magic with xkeyval to go over the 9-argument limit of LaTeX
\makeatletter
\define@key{Ex}{D}{#1}
\define@key{Ex}{d}{#1}
\define@key{Ex}{E}{#1}
\define@key{Ex}{l}{#1}
\define@key{Ex}{c}{#1}
\makeatother

% Frame, layer, and filler: the general macro
\makeatletter
\newcommandx{\prim}[6][2=,3=,4=,5=,6=]{\ensuremath{\mathsf{\color{indian-yellow}{#1}}_{#2}^{\joinargs{}[#3][#4][#5]}\@ifstar{}{\setkeys*{Ex}{#6}}}}
\makeatother

% Restriction for frame, layer, and filler: the general macro
\makeatletter
\newcommandx{\restr}[8][2=,3=,4=,5=,6=,7=,8=]{\ensuremath{\mathsf{\color{russian-green}{restr}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4]}^{\joinargs{}[#5][#6][#7]}\@ifstar{}{\setkeys*{Ex}{#8}}}}
\makeatother

@@

% Hack: we'd like \coh to take 10 arguments, with the 10th being passed to
% xkeyval, but this is not possible. The only possible compromise is to join
% #7, and #8 by hand in usage of \coh, by hand.
\makeatletter
\newcommandx{\coh}[9][2=,3=,4=,5=,6=,7=,8=,9=]{\ensuremath{\mathsf{\color{chestnut}{coh}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4][#5][#6]}^{\joinargs{}[#7][#8]}\@ifstar{}{\setkeys*{Ex}{#9}}}}
\makeatother

% Some abbreviations
\newcommand{\imp}{\ensuremath{\rightarrow}}
\newcommand{\overright}[1]{\ensuremath{\overrightarrow{#1}}}
\renewcommand{\D}{\ensuremath{(D)}}
\newcommand{\hdD}{\ensuremath{(D.1)}}
\newcommand{\tlD}{\ensuremath{(D.2)}}
\renewcommand{\d}{\ensuremath{(d)}}
\newcommand{\E}{\ensuremath{(E)}}
\renewcommand{\l}{\ensuremath{(l)}}
\renewcommand{\c}{\ensuremath{(c)}}

@@

% For just the first table, keep the universe letter in fullframe
\newcommandx{\fullframe}[2][1=,2=]{\prim{fullframe}[#1][#2][][]}
\input{tab-core.tex}

% Drop the universe letter in fullframe for all remaining tables
\renewcommandx{\fullframe}[2][1=,2=]{\prim{fullframe}[][#2][][]}
\input{tab-frames.tex}

@@

% Frame, layer, and filler
% Drop all arguments for coh table; they're not present in coind table.
\renewcommandx{\framep}[5][1=,2=,3=,4=,5=]{\prim{frame}[][][][][]}
\renewcommandx{\layer}[5][1=,2=,3=,4=,5=]{\prim{layer}[][][][][]}
\renewcommandx{\filler}[5][1=,2=,3=,4=,5=]{\prim{filler}[][][][][]}

@@

\newpage
\appendix
\section{Tables in full detail}
% Keep all arguments for all macros
% Frame, layer, and filler
\renewcommandx{\framep}[5][1=,2=,3=,4=,5=]{\prim{frame}[#1][#2][#3][#4][#5]}
\renewcommandx{\layer}[5][1=,2=,3=,4=,5=]{\prim{layer}[#1][#2][#3][#4][#5]}
\renewcommandx{\filler}[5][1=,2=,3=,4=,5=]{\prim{filler}[#1][#2][#3][#4][#5]}
\renewcommandx{\fullframe}[2][1=,2=]{\prim{fullframe}[#1][#2][][]}

>>>>

% Magic with xkeyval to go over the 9-argument limit of LaTeX
\makeatletter
\define@cmdkey{X}{D}{(#1)}

\define@cmdkey[prim]{frame}{D}{(#1)}
\define@cmdkey[prim]{layer}{D}{(#1)}
\define@cmdkey[prim]{layer}{d}{(#1)}
\define@cmdkey[prim]{filler}{D}{(#1)}
\define@cmdkey[prim]{filler}{E}{(#1)}
\define@cmdkey[prim]{filler}{d}{(#1)}
\define@cmdkey[prim]{fullframe}{D}{(#1)}

\define@cmdkey[restr]{frame}{D}{(#1)}
\define@cmdkey[restr]{frame}{d}{(#1)}
\define@cmdkey[restr]{layer}{D}{(#1)}
\define@cmdkey[restr]{layer}{d}{(#1)}
\define@cmdkey[restr]{layer}{l}{(#1)}
\define@cmdkey[restr]{filler}{D}{(#1)}
\define@cmdkey[restr]{filler}{E}{(#1)}
\define@cmdkey[restr]{filler}{d}{(#1)}
\define@cmdkey[restr]{filler}{c}{(#1)}

\define@cmdkey[coh]{frame}{D}{(#1)}
\define@cmdkey[coh]{frame}{d}{(#1)}
\define@cmdkey[coh]{layer}{D}{(#1)}
\define@cmdkey[coh]{layer}{d}{(#1)}
\define@cmdkey[coh]{layer}{l}{(#1)}
\define@cmdkey[coh]{filler}{D}{(#1)}
\define@cmdkey[coh]{filler}{E}{(#1)}
\define@cmdkey[coh]{filler}{d}{(#1)}
\define@cmdkey[coh]{filler}{c}{(#1)}
\makeatother

% Truncated sets, otherwise referred to as X: the general macro
\newcommandx{\X}[3][1=,2=,3=]{\ensuremath{\mathsf{\color{carolina}{X}}_{#1}^{#2}{\setkeys*{X}{#3}}}}

% Frame, layer, and filler: the general macro
\newcommandx{\prim}[6][2=,3=,4=,5=,6=]{\ensuremath{\mathsf{\color{indian-yellow}{#1}}_{#2}^{\joinargs{}[#3][#4][#5]}{\setkeys*[prim]{#1}{#6}}}}

% Restriction for frame, layer, and filler: the general macro
\newcommandx{\restr}[8][2=,3=,4=,5=,6=,7=,8=]{\ensuremath{\mathsf{\color{russian-green}{restr}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4]}^{\joinargs{}[#5][#6][#7]}{\setkeys*[restr]{#1}{#8}}}}

@@

% Hack: we'd like \coh to take 10 arguments, with the 10th being passed to
% xkeyval, but this is not possible. The only possible compromise is to join
% #7 and #8 by hand in usage of \coh: it's now #7 or '#6,#7' in \cohfoo commands
\newcommandx{\coh}[9][2=,3=,4=,5=,6=,7=,8=,9=]{\ensuremath{\mathsf{\color{chestnut}{coh}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4][#5][#6]}^{\joinargs{}[#7][#8]}{\setkeys*[coh]{#1}{#9}}}}

% Some abbreviations
\newcommand{\imp}{\ensuremath{\rightarrow}}
\newcommand{\overright}[1]{\ensuremath{\overrightarrow{#1}}}
\renewcommand{\D}{\ensuremath{D}}
\newcommand{\hdD}{\ensuremath{D.1}}
\newcommand{\tlD}{\ensuremath{D.2}}
\renewcommand{\d}{\ensuremath{d}}
\newcommand{\E}{\ensuremath{E}}
\renewcommand{\l}{\ensuremath{l}}
\renewcommand{\c}{\ensuremath{c}}
\newcommand{\pair}[2]{\ensuremath{#1, #2}}

@@

% For just the first table, keep the universe letter in fullframe
\newcommandx{\fullframe}[3][1=,2=,3=]{\prim{fullframe}[#1][#2][][][#3]}
\input{tab-core.tex}

% Drop the universe letter in fullframe for all remaining tables
\renewcommandx{\fullframe}[3][1=,2=,3=]{\prim{fullframe}[][#2][][][#3]}
\input{tab-frames.tex}

@@

% Frame, layer, and filler
% Drop all arguments for coh table; they're not present in coind table.
\renewcommandx{\framep}[5][1=,2=,3=,4=,5=]{\prim{frame}[][][][][#5]}
\renewcommandx{\layer}[5][1=,2=,3=,4=,5=]{\prim{layer}[][][][][#5]}
\renewcommandx{\filler}[5][1=,2=,3=,4=,5=]{\prim{filler}[][][][][#5]}

@@

\newpage
\appendix
\section{Tables in full detail}
% Keep all arguments for all macros
% Frame, layer, and filler
\renewcommandx{\framep}[5][1=,2=,3=,4=,5=]{\prim{frame}[#1][#2][#3][#4][#5]}
\renewcommandx{\layer}[5][1=,2=,3=,4=,5=]{\prim{layer}[#1][#2][#3][#4][#5]}
\renewcommandx{\filler}[5][1=,2=,3=,4=,5=]{\prim{filler}[#1][#2][#3][#4][#5]}
\renewcommandx{\fullframe}[3][1=,2=,3=]{\prim{fullframe}[#1][#2][][][#3]}
